Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-18 outputs/paper/paper.qmd
New figure added

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
# install.packages('here')
# install.packages("readstata13")  #  readstata13_0.9.2
# install.packages("MASS") # MASS_7.3-51.6  
# install.packages("sandwich")  # sandwich_2.5-1 
# install.packages("lmtest") # lmtest_0.9-37 
# install.packages("pBrackets") # pBrackets_1.0  
# install.packages("dplyr") 
# install.packages("tidyverse")

library(readr) # read_csv
library(here) # here
library(readstata13) #  readstata13_0.9.2
library(MASS) # MASS_7.3-51.6  
library(sandwich)  # sandwich_2.5-1 
library(lmtest) # lmtest_0.9-37  
library(dplyr)
library(tidyverse)
library(jtools)
library(huxtable)

@@

# Add value for mate competition tercile
s_exc$matecomp <- ifelse(s_exc$mate_compete >= 3, 1, 0)
s_exc$terc <- ifelse(s_exc$excess_males < 1.04, "1st Tercile", ifelse(s_exc$excess_males < 1.12, "2nd Tercile", "3rd Tercile"))

@@

# Calculating proportion 
mean_all <- tapply(s_exc$matecomp, s_exc$terc, mean)
mean_2 <- tapply(s_exc2$matecomp, s_exc2$terc, mean)
mean_3 <- tapply(s_exc3$matecomp, s_exc3$terc, mean)

@@

s_stmt <- survey_data[survey_data$wave == 2,]
s_stmt <- select(s_stmt, c(only_means, message, prevent, condemn, justified, list, treatment_list))

s_stmt$meansp <- ifelse(s_stmt$only_means >= 3, 1, 0)
s_stmt$msgp <- ifelse(s_stmt$message >= 3, 1, 0)
s_stmt$prevp <- ifelse(s_stmt$prevent >= 3, 1, 0)
s_stmt$justp <- ifelse(s_stmt$justified >= 3, 1, 0)

s_stmtmeans <- s_stmt %>% 
  na.omit(meansp)
meansp <- mean(s_stmt$meansp)
msgp <- mean(s_stmt$msgp)
prevp <- mean(s_stmt$prevp)
justp <- mean(s_stmt$justp)

>>>>

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
# install.packages('here')
# install.packages("readstata13")  #  readstata13_0.9.2
# install.packages("MASS") # MASS_7.3-51.6  
# install.packages("sandwich")  # sandwich_2.5-1 
# install.packages("lmtest") # lmtest_0.9-37 
# install.packages("pBrackets") # pBrackets_1.0  
# install.packages("dplyr") 
# install.packages("tidyverse")
# install.packages("list)

library(readr) # read_csv
library(here) # here
library(readstata13) #  readstata13_0.9.2
library(MASS) # MASS_7.3-51.6  
library(sandwich)  # sandwich_2.5-1 
library(lmtest) # lmtest_0.9-37  
library(dplyr)
library(tidyverse)
library(jtools)
library(huxtable)
library(list)

@@

# Add indicator if respondent agrees/strongly agrees that refugees are mate threats
s_exc$matecomp <- ifelse(s_exc$mate_compete >= 3, 1, 0)

# Add value for mate competition tercile
s_exc$terc <- ifelse(s_exc$excess_males < 1.04, "1st Tercile", ifelse(s_exc$excess_males < 1.12, "2nd Tercile", "3rd Tercile"))

@@

# Calculating proportion of respondents who agree or strongly agree by tercile
mean_all <- tapply(s_exc$matecomp, s_exc$terc, mean)
mean_2 <- tapply(s_exc2$matecomp, s_exc2$terc, mean)
mean_3 <- tapply(s_exc3$matecomp, s_exc3$terc, mean)

@@

# Set up, filter for wave 2 and select needed columns
survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))

s_stmt <- survey_data[survey_data$wave == 2,]
s_stmt <- select(s_stmt, c(only_means, message, prevent, condemn, justified))

# Add column with value for people agreeing or strongly agreeing
s_stmt$meansp <- ifelse(s_stmt$only_means >= 3, 1, 0)
s_stmt$msgp <- ifelse(s_stmt$message >= 3, 1, 0)
s_stmt$justp <- ifelse(s_stmt$justified >= 3, 1, 0)
s_stmt$prevp <- ifelse(s_stmt$prevent >= 3, 1, 0)
s_stmt$conp <- ifelse(s_stmt$condemn >= 3, 1, 0)

# Calculate proportion of respondents to agree/strongly agree with given statement
s_stmtmeans <- na.omit(s_stmt$meansp)
meansp <- mean(s_stmtmeans)

msgp <- mean(s_stmt$msgp)
justp <- mean(s_stmt$justp)
prevp <- mean(s_stmt$prevp)
conp <- mean(s_stmt$conp)

# Data frame prepped for plotting
s_stmt_p <- data.frame(c(meansp, msgp, justp, prevp, conp))
s_stmt_p$stmt <- c("Only means", "Message", "Justified", "Prevent", "Condemn")

colnames(s_stmt_p) <- c("pptn", "stmt")

s_stmt_p %>% 
  ggplot(aes(x=stmt, y=pptn)) +
  geom_col(fill="gray", colour="black") +
  scale_x_discrete(limits = c("Only means", "Message", "Justified", "Prevent", "Condemn")) +
  labs(x="Statement") +
  labs(y = wrapper("Proportion of respondents", width = 40)) +
  theme_minimal() +
  theme(text=element_text(size=11, family="serif")) +
  ggtitle(wrapper("13% to 25% of respondents agree with statements supporting or not condemning violence against refugees", width =60)) +
  theme(plot.title = element_text(face = "bold"))

# add note for condemn
```
